### 2022-04-03 README.Rmd
should be pretty stable: to CRAN?

Categorical             |  Sequential | Diverging
:-------------------------:|:-------------------------:|:-------------------------:
[![](https://user-images.githubusercontent.com/2444081/156847689-7e1a4608-9b03-45f5-9ccf-56e6d8844d47.png)](https://user-images.githubusercontent.com/2444081/156847689-7e1a4608-9b03-45f5-9ccf-56e6d8844d47.png) | [![](https://user-images.githubusercontent.com/2444081/156847703-b429c521-89d5-4e14-85c1-0f100ca93b45.png)](https://user-images.githubusercontent.com/2444081/156847703-b429c521-89d5-4e14-85c1-0f100ca93b45.png) | [![](https://user-images.githubusercontent.com/2444081/156847712-33a3cd22-a50b-44e2-9666-b67fcb0d2853.png)]((https://user-images.githubusercontent.com/2444081/156847712-33a3cd22-a50b-44e2-9666-b67fcb0d2853.png))

Color palettes are well organized and made consistent with each other. Moreover, they are scored on several aspects: color-blind-friendliness, the presence of intense colors (which should be avoided), the overall aesthetic harmony, and how many different hues are used. Finally, for each color palette a color for missing values is assigned, which is especially important for spatial data visualization. Currently we support several types: *categorical* (qualitative) palettes, *sequential* palettes, *diverging* palettes, and *bivariate* palettes (divided into three types). In the near future, more palette types may be added, such as *cyclic* and *hierarchical*.

@@

```{r, eval=FALSE}
# install.packages("devtools")
devtools::install_github("mtennekes/cols4all")
```

```{r, echo=FALSE}
getwd()
devtools::load_all(".")
```

@@

```{r, eval=FALSE}
library(cols4all)
# For the GUI, shiny, shinyjs, and kableExtra are required
# install.packages(c("shiny", "shinyjs", "kableExtra"))
c4a_gui()
```

Besides browsing through palettes, it is also easy to copy color codes to the clipboard, either by selecting the hidden text in the color tables or by clicking on the icons at the right-hand-side:

![](https://user-images.githubusercontent.com/2444081/156849917-59af1dc1-ee5e-40be-bf87-5c7384351ae0.png){width=50%}

@@

* It will be possible to submit an own series of color palettes.

@@

* Do you miss certain palettes or series?

>>>>

Categorical             |  Sequential | Diverging
:-------------------------:|:-------------------------:|:-------------------------:
[![](https://user-images.githubusercontent.com/2444081/161420545-68c007d1-640e-47f1-84e3-1e22c7b74e20.png)](https://user-images.githubusercontent.com/2444081/161420545-68c007d1-640e-47f1-84e3-1e22c7b74e20.png) | [![](https://user-images.githubusercontent.com/2444081/161420541-1c2dfefc-0451-47ed-badd-d5ecc339ead0.png)](https://user-images.githubusercontent.com/2444081/161420541-1c2dfefc-0451-47ed-badd-d5ecc339ead0.png) | [![](https://user-images.githubusercontent.com/2444081/161420543-62bc6947-df35-43e2-8277-35b2dbc223ca.png)]((https://user-images.githubusercontent.com/2444081/161420543-62bc6947-df35-43e2-8277-35b2dbc223ca.png)) |

Bivariate (seq x seq)		|  Bivariate (seq x cat)	|		Bivariate (seq x desaturated)
:-------------------------:|:-------------------------:|:-------------------------:
[![](https://user-images.githubusercontent.com/2444081/161420551-84475286-5394-4379-abfc-d765567c2db6.png)]((https://user-images.githubusercontent.com/2444081/161420551-84475286-5394-4379-abfc-d765567c2db6.png)) | [![](https://user-images.githubusercontent.com/2444081/161420550-dc0ac110-ddea-4f02-8d47-cbb6221cca4f.png)]((https://user-images.githubusercontent.com/2444081/161420550-dc0ac110-ddea-4f02-8d47-cbb6221cca4f.png)) | [![](https://user-images.githubusercontent.com/2444081/161420549-8130172f-9047-48c3-b8f5-1a3e7ae7c3b3.png)]((https://user-images.githubusercontent.com/2444081/161420549-8130172f-9047-48c3-b8f5-1a3e7ae7c3b3.png))

Color palettes are well organized and made consistent with each other. Moreover, they are scored on several aspects: color-blind-friendliness, the presence of intense colors (which should be avoided), the overall aesthetic harmony, and how many different hues are used. Finally, for each color palette a color for missing values is assigned, which is especially important for spatial data visualization. Currently we support several types: *categorical* (qualitative) palettes, *sequential* palettes, *diverging* palettes, and *bivariate* palettes (divided into three subtypes).

@@

```{r, eval=FALSE}
# install.packages("devtools")
remotes::install_github("mtennekes/cols4all")
```

```{r, echo=FALSE, message=FALSE}
devtools::load_all(".")
```

@@

```{r, eval=FALSE}
library(cols4all)
c4a_gui()
```

@@

* It is be possible to submit own color palettes.

@@

* Do you miss certain palettes?
